Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2024-02-15 paper/main.tex
Kush first pass, fix typos

To understand how our approach compares with state of the art large language models (LLM), we prompted GPT-4 to generate a mutation testing tool for Haskell.
Surprisingly, the generated program had no syntax errors, and even ran to produce a mutant. However, the program only implemented
the inverting conditionals operation and some basic module mutations,
a small subset of all the operators our tool implements, despite our
tool being unaware of Haskell's existence.. Asking the LLM to expand the set of rules
 produces more operators; however the number of mutants generated by
 such an approach is still a small subset of what our approach is
 capable of doing, even for a language we do not technically support.

@@

Our study only examined 24 total source files, from 24 different projects, across four different
languages, a total of about 9,000 lines of non-comment source code .  None of these files were very large, though they were of
sizes common to many source files in projects across GitHub, and none
were less than about 100 non-comment lines of code.  More importantly,
there is no established way to compare mutation tools.
Previous studies of the topic have generally simply expected that a
useful tool must
generate a significant number of non-equivalent unkilled mutants, and
yield mutation scores that are broadly similar to those of other
tools, both tests that our tool passes with ease (and some tools we
compared to do not always pass).

>>>>

To understand how our approach compares with state of the art large language models (LLM), we prompted GPT-4 to generate a mutation testing tool for Haskell.
Surprisingly, the generated program had no syntax errors, and even ran to produce a mutant. However, the program only implemented
the inverting conditionals operation and some basic module mutations,
a small subset of all the operators our tool implements, despite our
tool being unaware of Haskell's existence. Asking the LLM to expand the set of rules
 produces more operators; however the number of mutants generated by
 such an approach is still a small subset of what our approach is
 capable of doing, even for a language we do not technically support.

@@

Our study only examined 24 total source files, from 24 different projects, across four different
languages, a total of about 9,000 lines of non-comment source code.  None of these files were very large, though they were of
sizes common to many source files in projects across GitHub, and none
were less than about 100 non-comment lines of code.  More importantly,
there is no established way to compare mutation tools.
Previous studies of the topic have generally simply expected that a
useful tool must
generate a significant number of non-equivalent unkilled mutants, and
yield mutation scores that are broadly similar to those of other
tools, both tests that our tool passes with ease (and some tools we
compared to do not always pass).
